### 2017-01-09 README.Rmd
Add CRAN badge
Try to get badges on same line

[![Build Status](https://travis-ci.org/geanders/futureheatwaves.svg?branch=master)](https://travis-ci.org/geanders/futureheatwaves)

>>>>

[![Build Status](https://travis-ci.org/geanders/futureheatwaves.svg?branch=master)](https://travis-ci.org/geanders/futureheatwaves)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/futureheatwaves)](https://cran.r-project.org/package=futureheatwaves)
